{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-16 bmvc_review.tex
Table Updated with R_S and R_L
Revised the draft between experiments and conclusion.

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing specific challenges in single,
target tracking problem. Thus each of them should have different
values for the optimal parameters. For instance, the primary task of
the translation filter, $R_{t}^{L}$ is to estimate the translation of
a target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter update
threshold, $T_{R_{s}}$, to 4. For our particle filter implementation, we
empirically set the number of particles to $1000$ to balance the
run-time performance and accuracy. To keep the level of variance among
the particles reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

\textbf{Features Selections} As each of three KCFs in the {\it E}nKCF
has different goals to accomplish, we used different features for each
of them. In particular, the translation filter, $R_{t}^{L}$, uses both
the fast Histograms of Oriented Gradients (fHoG)
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the background around the target more
effectively. In fact we empirically found fHoG only didn't work well
to cover the larger ROI. Another translation filter, $R_{t}^{S}$, used
fHoG features only. The scale filter, $R_{s}$ used both fHoG and color
features to learn the scale change more accurately.

\textbf{Performance on UAV123 Dataset} We compared the performance of
the proposed algorithm with those of the state-of-the-art high speed
tracking algorithms by the \textit{Precision} and \textit{Success\:Rate} metrics. 
For the precision, we rank the trackers based on the precision numbers at 20 pixels 
whereas in the success rate plots, trackers are ranked based on area under curve
(AUC) scores. The tracking algorithms used for the comparison include
ones in high-speed ($\geq$300 fps), i.e., KCF\cite{henriques2015high},
CSK \cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50), i.e., SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels precision
metric. Three algorithms, SAMF, DSST, and Struck did about 5\% better
than ours in accuracy, but 10-20 times slower than ours. For the scale
adaptation, {\it E}nKCF did second best in terms of \textit{area under
  curve} (AUC) value for the success rate plot. It outperformed other
tracking methods in high-speed by about $20\%$-$25\%$ in AUC
metric. In addition, it performed even better than those algorithms
that are slow, but a bit better in precision. For example, for AUC,
{\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while
running at more than $10$ and $30$ times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny \textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

We also compare the proposed {\it E}nKCF tracker to the LCT \cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}. 
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$,  $R_{s}$) in  {\it E}nKCF, we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ with similar
run-time performance. On the other hand, we employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as we run filters in every frame. Running another filter, 
$R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
tracker ({\it m}LCT) and run $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given order. $R_{t}^{S}$ uses the translation estimation given by $R_{t}^{L}$ to update
translation and $R_{s}$ uses the final translation estimation given by $R_{t}^{S}$ to update scale. Interestingly, running two complementary translation filter results in significant improvement
at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
high speed but also more accurate tracker than the baseline methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run the filters in every frame in the listed order. The LCT tracker \cite{ma2015long} runs a translation and scale filter in every frame (similar to $6^{th}$ method) and couples a re-detection method to perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

>>>>

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing specific challenges in single,
target tracking problem. Thus each of them should have different
values for the optimal parameters. For instance, the primary task of
the translation filter, $R_{t}^{L}$ is to estimate the translation of
a target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. For our particle filter implementation, we empirically set the
number of particles to $1000$ to balance the run-time performance and
accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

\textbf{Features Selections} We used different features for each of
three KCFs as each of them has different goals to accomplish. In
particular, the translation filter, $R_{t}^{L}$, uses both the fast
Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
and color-naming \cite{van2009learning} features to learn the
background around the target more effectively. However we found,
through experiments, that only fHoG didn't work well to cover a larger
ROI. In a same way, we found that another translation filter,
$R_{t}^{S}$, worked well when it used fHoG features only and the scale
filter, $R_{s}$ did when it used both fHoG and color features.

\textbf{Performance on UAV123 Dataset} We compared, using the
precision and success rate metrics, the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50): SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
MUSTER \cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ in 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny \textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

{\it Burak: Remove LCT part!}

We also compare the proposed {\it E}nKCF tracker to the LCT
\cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}.  By
using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ with similar run-time performance. On the other hand, we
employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as
we run filters in every frame. Running another filter, $R_{t}^{L}$ or
$R_{t}^{S}$, in the {\it E}nKCF framework not only gives us
significantly higher run-time performance but also higher
accuracy. Finally, we modify the LCT tracker ({\it m}LCT) and run
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given
order. $R_{t}^{S}$ uses the translation estimation given by
$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In conclusion, running two complementary translation
filter and a scale filter in the {\it E}nKCF framework not only
provides high speed but also more accurate tracker than the baseline
methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed
  KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of
  $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
  method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the
  $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run
  the filters in every frame in the listed order. The LCT tracker
  \cite{ma2015long} runs a translation and scale filter in every frame
  (similar to $6^{th}$ method) and couples a re-detection method to
  perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}
